A novel route to the spontaneous formation of porous crystals via viscoelastic phase separation

### 2016-06-21 talk_Roscoff.tex
Experimental: whole process, 10^4 particles, from t=0, to t>10^4 tau_B
fix nuclei size distribution

\begin{frame}{Experimental}
How to do that in 3D at particle level \alert{without a space station}?
\begin{itemize}
\item index matched + \alert{\SI{2.3}{\micro\metre} colloids} + confocal
\item density match + $T$-control
\item preparation protocol without flow
\end{itemize}
\bigskip
\begin{columns}
	\column{0.265\textwidth}
		Colloids+polymers\\
		{\footnotesize no screening
		\begin{itemize}
			\item Dispersed
			\item Homogeneous
		\end{itemize}
		\bigskip
		\begin{beamercolorbox}[rounded=true]{block body}PMMA + PS\\
		in decalin + CHB $\epsilon_r\approx5$\\
		$\kappa^{-1}>\SI{10}{\micro\metre}$
		\end{beamercolorbox}}
	\column{0.4\textwidth}
		\tikzsetnextfilename{chemin_gelification}%
		\input{presentation/chemin_gelification.pgf}
	\column{0.335\textwidth}
		\tikzsetnextfilename{cell}%
		\input{presentation/cell.pgf}
\end{columns}
\end{frame}

@@

		\nextgroupplot[
			title={cluster size distribution},
			xlabel={$s$}, ylabel=$R_g/\sigma$,
			xmode=log, ymode=log,
			ytick={0.5, 1, 2, 4}, yticklabels={$\frac{1}{2}$, 1, 2, 4},
			domain=1:5e2,
			]
		\addplot[only marks, red, thick, mark=*] file{data/fig3d_sqrt_1.dat};
		\addplot[black, ultra thick] {0.522*x^(1/3)} node[below left] at (axis cs:9e2,2.5) {$D=3$};
		\addplot[gray, ultra thick] {0.426*x^(1/2.53)} node[pos=0.08,below right] {$D=2.53$};
	\end{groupplot}
	\end{tikzpicture}

>>>>

\begin{frame}{Experimental}
	\vspace{\baselineskip}
	How to observe the whole process in 3D at particle level?
	\begin{itemize}
		\item index matched + \alert{\SI{2.3}{\micro\metre} colloids} + confocal
		\item density match + $T$-control
		\item preparation protocol without flow
	\end{itemize}
	\bigskip
	\begin{columns}
		\column{0.265\textwidth}
			Colloids+polymers\\
			{\footnotesize no screening
			\begin{itemize}
				\item Dispersed
				\item Homogeneous
			\end{itemize}
			\bigskip
			\begin{beamercolorbox}[rounded=true]{block body}PMMA + PS\\
			in decalin + CHB $\epsilon_r\approx5$\\
			$\kappa^{-1}>\SI{10}{\micro\metre}$
			\end{beamercolorbox}}
		\column{0.4\textwidth}
			\tikzsetnextfilename{chemin_gelification}%
			\input{presentation/chemin_gelification.pgf}
		\column{0.335\textwidth}
			\tikzsetnextfilename{cell}%
			\input{presentation/cell.pgf}
			\vspace{-\baselineskip}
			\begin{itemize}
			\item $\sim 10^4$ particles
			\item from $t=0$
			\item to $t>10^4\tau_B$
			\end{itemize}
	\end{columns}
\end{frame}

@@

		\nextgroupplot[
			title={nuclei size distribution},
			xlabel={$s$}, ylabel=$R_g/\sigma$,
			xmode=log, ymode=log, ymin=0.3,
			ytick={0.5, 1, 2, 4}, yticklabels={$\frac{1}{2}$, 1, 2, 4},
			domain=1.1:5e2,
			]
		\draw[dashed] (rel axis cs:0.5,0) -- (rel axis cs:0.5,1);
		\addplot[only marks, red, thick, mark=*] file{data/fig3d_sqrt_1.dat};
		\addplot[black, ultra thick] {0.522*x^(1/3)} node[below left] at (axis cs:9e2,2.5) {$D=3$} node[anchor=north east, font=\footnotesize, text width=0.1\textwidth] at (rel axis cs:1,0.5) {outgrow\linebreak network};
		\addplot[gray, ultra thick] {0.426*x^(1/2.53)} node[anchor=south west, inner sep=1pt] at (rel axis cs:0,0){$D=2.53$} node[anchor=north east, font=\footnotesize, text width=0.2\textwidth, align=right] at (rel axis cs:0.45,1) {within\linebreak network};

	\end{groupplot}
	\end{tikzpicture}
